Methods

### 2019-01-23 Methods.Rmd
working_bits

This code is testing out the wavelet analyses for the in situ temperature data

```{r}
SACTN_wavelet <- SACTN_daily_temps_indexsplit %>% 
  filter(year(date) %in% seq(2015, 2016))

SACTN_wavelet.d <- SACTN_wavelet %>% 
  dplyr::group_by(site, date) %>% 
  dplyr::summarise(temp = mean(insitu_temp, na.rm = TRUE)) %>% 
  dplyr::mutate(no = seq(1:n())) %>%
  dplyr::ungroup() %>% 
  dplyr::select(site, no, temp, date)

ggplot(data = SACTN_wavelet, aes(x = date, y = insitu_temp)) +
  geom_hline(aes(yintercept = mean(insitu_temp)), colour = "salmon") +
  geom_line() +
  facet_wrap(~ site, nrow = 4) +
  theme_bw()

auto.arima(dplyr::filter(SACTN_wavelet, site == "Port Nolloth")[, "insitu_temp"], max.p = 3, max.q = 3, stationary = FALSE, 
           seasonal = FALSE)

PN <- SACTN_wavelet.d %>% 
  dplyr::filter(site == "Port Nolloth") %>% 
  dplyr::select(temp, -date, -site) %>% 
  dplyr::mutate(no = seq(1:n())) %>% 
  dplyr::select(no, temp)
```

@@

@@

@@

@@

To explore the data i visualise the min temperatures along the South african coastline.

@@

OISST_sites <- OISST_sites %>% 
  dplyr::rename(temp = temp_OISST)
```

@@

```{r}
OISST_plot <- match_plot(df = OISST_sites)
```

##

>>>>

@@

```{r}
ggplot(data = SACTN_3yr, aes(x = date, y = insitu_temp, colour = site)) +
geom_line(aes(group = site)) +
labs(x = "", y = "Temperature (°C)") +
theme(axis.text.x = element_text(angle = 45)) +
theme_linedraw() +
theme(legend.position = "top")
```

@@

insitu_MUR <- match_func(df = MUR_SST) %>%
  drop_na()

@@

```{r}
ggplot(data = insitu_MUR, aes(x = date, y = temp, colour = site)) +
geom_line(aes(group = site)) +
labs(x = "", y = "Temperature (°C)") +
theme(axis.text.x = element_text(angle = 45)) +
theme_linedraw() +
theme(legend.position = "top")
```

@@

To explore the data I visualise the min temperatures along the South african coastline.

@@

OISST_sites <- OISST_sites %>% 
  dplyr::rename(temp = temp_OISST) %>%
  dplyr::mutate(date = as.Date(date)) %>% 
  drop_na()
```

@@

```{r}
OISST_plot <- match_plot(df = insitu_OISST)
```

```{r}
ggplot(data = insitu_OISST, aes(x = date, y = temp, colour = site)) +
geom_line(aes(group = site)) +
labs(x = "", y = "Temperature (°C)") +
theme(axis.text.x = element_text(angle = 45)) +
theme_linedraw() +
theme(legend.position = "top")
```
